PHAT RAID, yo

### 2014-05-15 paper/paper.tex
more hd stuff

An important consideration in our project is the impact disk performance has on overall commit latency. We believe that disk read/write latency is the major contributor to storing large files in a distributed system. {\bf TODO more}

@@

\urldef\hwbenchmark\url{http://www.tomshardware.com/charts/ssd-charts-2013/benchmarks%2C129.html}
\begin{figure}
\centering
\begin{tabular}{l || c}
\multicolumn{2}{c}{{\bf Solid State Disk Performance Benchmarks}} \\ \hline
Sequential Write Speed  \hspace{7em} & 55.03 - 481.85 MB/sec \\ 
Write Access Time & 0.03 - 0.32 ms \\ \hline
Sequential Read Speed &  207.95 - 522.45 MB/sec \\
Read Access Time & 0.03 - 0.22 ms \\ \hline
\end{tabular}
\caption[Solid State Performance]{Solid State Disk performance for middle 95\% of solid state drives tested in a benchmark. Benchmark available at Benchmark available at \hwbenchmark.}
\label{fig:sdd-perf}
\end{figure}

Figure \ref{fig:sdd-perf} shows the performance for SSDs from a 2013 survey of commercially available SSDs. Sequential write speeds measure the throughput (in megabytes per second) of data stored on the drive when the data is being written in the drive's natural sequential order (e.g. increasing sectors). Similarly, sequential read speed measures the throughput for sequential reads. Read/Write access times represent the latency of performing a single random read or write.

@@

We developed a novel ``{\bf {\em Disk Emulation and Abstraction Layer}}'' (DEAL)
to simulate SSD performance so they .

>>>>

An important consideration in our project is the impact disk performance has on overall commit latency. We believe that disk read/write latency is the major contributor to storing large files in a distributed system.

@@

\urldef\hwbenchmark\url{http://www.tomshardware.com/charts/ssd-charts-2013/benchmarks%2C129.html}
\begin{figure}
\centering
\begin{tabular}{l || c}
\multicolumn{2}{c}{{\bf Solid State Disk Performance Benchmarks}} \\ \hline
Sequential Write Speed  \hspace{7em} & 55.03 - 481.85 MB/sec \\ 
Write Access Time & 0.03 - 0.32 ms \\ \hline
Sequential Read Speed &  207.95 - 522.45 MB/sec \\
Read Access Time & 0.03 - 0.22 ms \\ \hline
\end{tabular}
\caption[Solid State Performance]{Solid State Disk performance for middle 95\% of solid state drives tested in a benchmark. Benchmark available at Benchmark available at \hwbenchmark.}
\label{fig:ssd-perf}
\end{figure}

Figure \ref{fig:ssd-perf} shows the performance for SSDs from a 2013 survey of commercially available SSDs. Sequential write speeds measure the throughput (in megabytes per second) of data stored on the drive when the data is being written in the drive's natural sequential order (e.g. increasing sectors). Similarly, sequential read speed measures the throughput for sequential reads. Read/Write access times represent the latency of performing a single random read or write.

@@

We developed a novel ``{\bf {\em Disk Emulation and Abstraction Layer}}'' (DEAL)
to simulate SSD performance for our evaluation. The DEAL simulates read and 
write delay using the information from Figure \ref{fig:ssd-perf}. We calculate disk delay as:

\begin{align}
\textsc{ReadDelay}(x) =&\ x / \textsc{SeqReadSpeed} + \textsc{ReadAccessTime}\\
\textsc{WriteDelay}(x) =&\ x / \textsc{SeqWriteSpeed} + \textsc{WriteAccessTime}
\end{align}

where $x$ is the size of the file. During filesystem operations, these formulas are
used to put the process to sleep in proportion to the size of the file being written to
or read from the drive.

Instead of sending very large files, we sent smaller strings that were treated by the 
DEAL as being much larger (e.g. 1 character represented 1MB of data). As a result,
we extended the DEAL to perform an additional delay for performing bitwise XOR
on file as that was the only operation on a file. In our model, drive delays were
much greater than XOR delays (e.g. 20 GB/second XOR delay versus 200 MB/second
drive delay).
